\mytitile\\~

### 2020-01-23 document.tex
Topo text color + minor DPT edits

The choice of zero-order state vectors $\ket{N^0}$ from a degenerate subspace is arbitrary because any linear combination of basis vectors $\ket{n}$ from this subspace will satisfy the unperturbed Schrödinger equation. However, if we demand the \textit{change} of $\ket{N^0}$ to be small under the perturbation $\hat V$, they become determined and are given by diagonalization of $\hat V$ in the degenerate subspace. Unfortunately, $\hat V$ is zero in both our subspaces, so technically any choice of zero-order states will diagonalize $\hat V$. In other words, the degeneracy is not lifted in the first-order, and thus we have diagonalize the matrix\cite{landau2013quantum}
\begin{equation}
	M_{nn'} = \sum\limits_{m}\frac{V_{ nm}V_{mn^\prime}}{E_n-E_m}.
\end{equation}
Here, $\ket{n}$ and $\ket{n'}$ are the basis 
states from the degenerate subspace with energy 
$E_n$, and $V_{mn} = \bra{m} \hat  V \ket{n}$. 
The sum is over all other zero-order states 
$\ket{m}$ outside the degenerate subspace.

>>>>

The choice of zero-order state vectors $\ket{N^0}$ from a degenerate subspace is arbitrary because any linear combination of basis vectors $\ket{n}$ from this subspace will satisfy the unperturbed Schrödinger equation. However, if we demand the \textit{change} of $\ket{N^0}$ to be small under the perturbation $\hat V$, they become determined and are given by diagonalization of $\hat V$ in the degenerate subspace. Unfortunately, all matrix elements of $\hat V = \hat V_J$ are zero in both our degenerate subspaces, so technically any choice of zero-order states will diagonalize it. In other words, the degeneracy is not lifted in the first-order, and thus we have to diagonalize the matrix\cite{landau2013quantum}
\begin{equation}
	M_{nn'} = \sum\limits_{m}\frac{V_{ nm}V_{mn^\prime}}{E_n-E_m}.
\end{equation}
Here, $\ket{n}$ and $\ket{n'}$ are the basis 
states from the degenerate subspace with energy 
$E_n$, and $V_{mn} = \bra{m} \hat  V \ket{n}$. 
The sum is over all other zero-order states 
$\ket{m}$ outside the degenerate subspace.
